\documentclass[11pt,twoside]{article}
\input{preamble}

\title{Liii STEM Input Method Cheatsheet}
\author{Liii Network}

\begin{document}

\maketitle

% \emph{Some keyboard shortcuts in this list may not be available on non-US keyboards or in vim/emacs modes. For example, some input methods on the Mac may use \keys{alt} (equivalent of {\setmenukeyswin\keys{alt}}) for accented characters input instead.}

\emph{\href{https://liiistem.cn/}{Liii STEM}~(\url{https://liiistem.cn/}) is a WYSIWYG editor that can speed up your mathematical writing by 10x. See \href{https://liiistem.com/docs/guide-equation.html}{Quick formula editing} for more details. This is a pdf version cheatsheet of the keys available in Liii STEM Input Method.}

\emph{Unlike the shorcut hints inside Liii STEM. We distinguish the capital and noncapital letters in this cheatsheet; For example, \keys{J} and \keys{j} are different. We also use \keys{\shift j} to replace \keys{J} where \keys{\shift} represents the \texttt{Shift} key.}

\emph{When no plus sign is shown between different keyboard keys, it means they should be pressed in sequence. Alternatively, a plus sign between them means they should be pressed at the same time. For modifier keys (and their combination such as \keys{ctrl \shift}) \keys{\shift}, \keys{ctrl}, \keys{alt} (Windows) or \keys{option} (Mac), and \keys{cmd} (Mac), the plus sign after them means to hold down the modifier key while pressing the next key. For example \keys{Ctrl + f 1} means to hold down the \keys{Ctrl} key and press the \keys{f} key and then press \keys{1} in sequence.}


\emph{All \keys{tab} keys represents tab varient. For example, to insert $\nabla$, press \keys{\shift v} and press \keys{tab} twice. To insert $\Phi$, press \keys{\shift v} and press \keys{tab} once. In the rest of this tutorial, we do specify the exact number of \keys{tab} we used, i.e., the keyboard expression for both \( \nabla \) and \( \Phi \) is \keys{shift v tab}.}


% \emph{The symbol \LaTeX\$ represents that the shortcut is only available in math mode.}




\bigskip

\begin{xltabular}{\textwidth}{
        >{\setmenukeyswin}c @{\hspace{2em}}
        >{\setmenukeysmac}c @{\hspace{2em}}
        >{\renewcommand\cellalign{cl}\RaggedRight\arraybackslash}X}


    \toprule
    \makecell{\sffamily Windows \faWindows\\\sffamily\textsc{gnu}/Linux \faLinux} & \sffamily Mac \faApple & \multicolumn{1}{c}{\sffamily  Equivalent in \LaTeX \faComment}\\
    \midrule
    \endfirsthead

    \footnotesize \faChevronCircleLeft\ (from previous page)\\[1em]
    \toprule
    \makecell{\sffamily Windows \faWindows\\\sffamily\textsc{gnu}/Linux \faLinux} & \sffamily Mac \faApple & \multicolumn{1}{c}{\sffamily Equivalent in  \LaTeX \faComment}\\
    \midrule
    \endhead

    \\[-1.5em]
    \multicolumn{3}{r}{\footnotesize (continued next page) \faChevronCircleRight}
    \endfoot
    \bottomrule
    \endlastfoot



    \input{docs/env_cut}
    \input{docs/Common_constructs}
    \input{docs/Font}
    \input{docs/greek}
    \input{docs/Sets_and_logic}
    \input{docs/Decorations }
    \input{docs/Dots }
    \input{docs/Other_symbles}
    \input{docs/Variable_sized_operators}
    \input{docs/Arrow}
    \input{docs/Fences}
\end{xltabular}


\end{document}